Malacology: A Programmable Storage System Built on Ceph

### 2016-05-09 paper/paper.tex
modified:   paper.tex 	Better formatting of contributions in intro

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item A programmable storage system implementation that re-uses and extends existing abstractions. It includes:

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    Extending file system metadata by a new type of ``sequencer'' inode that together with Ceph's capability subsystem implements high-performance, non-durable access serialization
  \item
    Re-using Ceph's PAXOS-based consensus infrastructure for versioning of metadata service load-balancing policies
  \item
    Re-using storage objects for persisting policies
  \item
    Extending object interface classes for new logical storage/metadata devices
  \end{enumerate}
\item
  Two example implementations and evaluations for feasibility of services that use this framework

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    A high-performance distributed shared log service called Zlog which is based on CORFU~\cite{balakrishnan_corfu_2012}
  \item
    A re-implementation of the programmable Mantle metadata load balancing service using Malacology~\cite{sevilla:sc15-mantle}
  \item 
    An application of the Mantle metadata load balancing service to manage the placement of new sequencer inodes.
  \end{enumerate}
\end{itemize}

>>>>

\paragraph*{A programmable storage system implementation} that re-uses and extends existing abstractions. It includes:

  \begin{enumerate}
%  \def\labelenumi{\arabic{enumi}.}
%  \itemsep1pt\parskip0pt\parsep0pt
  \item
    An extension of file system metadata by a new type of ``sequencer'' inode that together with Ceph's capability subsystem implements high-performance, non-durable access serialization
  \item
    The use of Ceph's PAXOS-based consensus infrastructure for versioning of metadata service load-balancing policies
  \item
    The use of storage objects for persisting policies
  \item
    An extension of the object interface classes for new logical storage/metadata devices
  \end{enumerate}

\paragraph*{Two example implementations and evaluations} for feasibility of services that use this framework

  \begin{enumerate}
%  \def\labelenumi{\arabic{enumi}.}
%  \itemsep1pt\parskip0pt\parsep0pt
  \item
    A high-performance distributed shared log service called Zlog which is based on CORFU~\cite{balakrishnan_corfu_2012}
  \item
    A re-implementation of the programmable Mantle metadata load balancing service~\cite{sevilla:sc15-mantle} using Malacology
  \item 
    An application of the Mantle metadata load balancing service to manage the placement of new sequencer inodes.
  \end{enumerate}
